Reviving the Lost Art of Combinator Graph Reduction

### 2022-12-19 experiments/superg/doc/paper/paper.tex
Write about linear algorithm.

\usepackage{amsmath}
\DeclareMathOperator{\strict}{strict}
\DeclareMathOperator{\lazy}{lazy}
\DeclareMathOperator{\lazyeta}{lazy_\eta}

@@

>>>>

\usepackage{amsmath}
\DeclareMathOperator{\strict}{strict}
\DeclareMathOperator{\lazy}{lazy}
\DeclareMathOperator{\lazyeta}{lazy_\eta}
\DeclareMathOperator{\linear}{linear}

@@

\subsection{Linear algorithm}
The implementation of the linear algorithm is much simpler because it is based on the strict algorithm.
The compilation function is identical save for a different semantic function $\coprod_{\text{linear}}$:

\begin{equation*}
    \begin{array}{l l l l}
        \linear & z         & = & 1 \models I                                                              \\
        \linear & s \ e     & = & n+1 \models (0 \models K) \coprod (n \models c)                          \\
                &           &   & \text{where } (n \models c) := \linear e                                 \\
        \\
        \linear & \lambda e & = & 0 \models K \; c                                                         \\
                &           &   & \text{where } (0 \models c) := \linear e                                 \\
        \linear & \lambda e & = & (n-1) \models K \; c                                                     \\
                &           &   & \text{where } (n \models c) := \linear e                                 \\
        \\
        \linear & e_1 \ e_2 & = & (n \models ((n_1 \models c_1) \coprod_{\text{linear}} (n_2 \models c_2)) \\
                &           &   & \text{where } (n_1 \models c_1) := \linear e_1                           \\
                &           &   & \text{where } (n_2 \models c_2) := \linear e_2                           \\
                &           &   & \text{where } n := \max n_1 \, n_2                                       \\
    \end{array}
\end{equation*}

below we give the corresponding semantic function, which is no longer recursive, making this algorithm linear:

\begin{equation*}
    \arraycolsep=1.4pt
    \begin{array}{l l l l l}
        (0 \models c_1)   & \coprod & (0 \models c_2)   & = & c_1 \ c_2                               \\
        \\
        (0 \models c_1)   & \coprod & (n \models c_2)   & = & B_n \ c_1 \ c_2                         \\
        \\
        (n \models c_1)   & \coprod & (0 \models c_2)   & = & C_n \ c_1 \ c_2                         \\
        \\
        (n \models c_1)   & \coprod & (n \models c_2)   & = & S_n \ c_1 \ c_2                         \\
        \\
        (n_1 \models c_1) & \coprod & (n_2 \models c_2) & = & B_{n_2-n_1} \ (S_{n_1} \ c_1) \ c_2     \\
                          &         &                   &   & \text{where } n_1 < n_2                 \\
        (n_1 \models c_1) & \coprod & (n_2 \models c_2) & = & C_{n_1-n_2} \ (B_{n_1-n_2} \ c_1) \ c_2 \\
                          &         &                   &   & \text{where } n_1 > n_2                 \\
    \end{array}
\end{equation*}

\textbf{TODO: } Can we add lazy weakening and/or eta optimization?
